Adaptive broadcast tree for multicores

### 2013-04-29 paper.tex
Better distinction from related work

Another tree implementation with MPI in mind was done
in~\cite{Graham2008}. They have comparable numbers to what we found.

>>>>

Another tree implementation with MPI in mind was done
in~\cite{Graham2008}. They have comparable numbers to what we found,
but they cannot automatically tune to different machine
characteristics. Our hypothesis is that we can do achieve higher
average performance across a wide range of different multicore
machines without manually adapting the implementation.
